\documentclass[11pt]{article}

% Expand margins
\addtolength{\oddsidemargin}{-.75in}
\addtolength{\evensidemargin}{-.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}
\linespread{1}

% Packages
\usepackage{comment}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{times}
\usepackage{xcolor}

\usepackage{color}
\definecolor{mygreen}{RGB}{84,158,57}

%\newenvironment{name}[num]{before}{after}

% New environments
\newenvironment{mysection}{
\color{mygreen}\bfseries\large
}
{
\\ \rule{\textwidth}{1pt}\hspace{-.25em}
} % \hspace{-.25em} eliminates extra white space

\begin{document}
\begin{center}
\begin{LARGE}Zachary Gardner\end{LARGE} \\
\vspace{1em}
\texttt{zachary.gardner@bc.edu} \\
(214) 493-7284 \\
U.S. Citizen \\
\end{center}

% ---
\begin{mysection}Education\end{mysection}
\textbf{Boston College} \hfill 2020-- \\
\textit{Ph.D. in Mathematics} \\

\textbf{University of Texas at Austin} \hfill 2016-2020 \\
\textit{B.S. in Mathematics with Departmental Honors} \\
Thesis: ``The Mordell-Weil Theorem for Abelian Varieties over Global Fields,'' advised by Sam Raskin \\
% ---

% ---
\begin{mysection}Teaching Experience\end{mysection}
\textbf{Boston College} \\
Teaching assistant for Math 331201 Algebra II \hfill Spring 2021 \\
Teaching assistant for Math 1102 Calculus I (Math/Sci) discussion sections 01, 02, 03 \hfill Fall 2020 \\

\textbf{University of Texas at Austin Summer Minicourses} \\
Instructor for ``Abelian Varieties and the Mordell-Weil Theorem'' \hfill Summer 2020 \\
Co-instructor for ``Class Field Theory'' \hfill Summer 2019 \\

\textbf{Ross USA Mathematics Program} \\
\textit{Algebraic Geometry Learning Group Leader} \hfill Fall 2019-Spring 2020 \\
Met every other weekend with Ross alumni to discuss algebraic geometry. \\
Led discussion, compiled exercises for group participants, and integrated other sources. \\

\textit{Long-Distance Counselor} \hfill Fall 2019 \\
Mentored one student from Summer 2019 program in proof writing, number theory, and abstract algebra. \\

\textit{Counselor} \hfill Summer 2019 \\
Graded and mentored five first-year students and two junior counselors in proof writing, number theory, and abstract algebra. \\
Ran training workshops for counselors and junior counselors. \\

\textit{Counselor} \hfill Summer 2017 \\
Graded and mentored four first-year students and one junior counselor in proof writing, number theory, and abstract algebra. \\
% ---

% ---
\begin{mysection}Service \& Outreach\end{mysection}
\textbf{Boston College} \\
Co-organizer for Arithmetic Geometry Learning Seminar \hfill Spring 2021 \\

\textbf{University of Texas at Austin} \\
Co-organizer for University of Texas at Austin Summer Minicourses \hfill Summer 2020 \\
Co-organizer for Basic Algebraic Geometry Seminar \hfill Spring 2020 \\
Co-organizer for Graduate Algebraic Geometry Seminar \hfill Fall 2019 \\
% ---

% ---
\begin{mysection}Scholarships, Honors, \& Awards\end{mysection}
\textbf{University of Texas at Austin} \\
CNS Dean's Honored Graduate \hfill Spring 2020 \\
CNS Service \& Leadership Distinction \hfill Spring 2020 \\
Barrett Fellowship \hfill Fall 2019 \\
Carmelina Cutro Albino Memorial Endowed Presidential Scholarship \hfill Spring 2018 \\
% ---

% ---
\begin{mysection}Conferences Attended\end{mysection}
\textbf{Boston Remote Seminar on Perfectoid Spaces} \hfill Jul. 21-Aug. 28, 2020 \\
% ---
\end{document}